Openness and computational reproducibility in plant pathology: where we stand and a way forward

### 2023-01-03 analysis/paper/paper.Rmd
Correct figure order and references in text

Additionally, data that supported the articles were mostly unavailable with `r length(which(rrpp$data_avail == 0))` (`r round(length(which(rrpp$data_avail == 0))/nrow(rrpp), 2) * 100`%) scoring '0' where the original data were not available or mentioned in the article.
However, more articles, `r length(which(rrpp$data_avail == 3))` (`r round(length(which(rrpp$data_avail == 3))/nrow(rrpp), 2) * 100`%), scored '3' than scored '1' or '2' combined, `r length(which(rrpp$data_avail == 2 | rrpp$data_avail == 1))` (`r round(length(which(rrpp$data_avail == 2 | rrpp$data_avail == 1))/nrow(rrpp), 2) * 100`%) with `r as.character(english(length(which(is.na(rrpp$data_avail)))))` articles not producing shareable data (Figure \@ref(fig:articleScores)D).

>>>>

Additionally, data that supported the articles were mostly unavailable with `r length(which(rrpp$data_avail == 0))` (`r round(length(which(rrpp$data_avail == 0))/nrow(rrpp), 2) * 100`%) scoring '0' where the original data were not available or mentioned in the article.
However, more articles, `r length(which(rrpp$data_avail == 3))` (`r round(length(which(rrpp$data_avail == 3))/nrow(rrpp), 2) * 100`%), scored '3' than scored '1' or '2' combined, `r length(which(rrpp$data_avail == 2 | rrpp$data_avail == 1))` (`r round(length(which(rrpp$data_avail == 2 | rrpp$data_avail == 1))/nrow(rrpp), 2) * 100`%) with `r as.character(english(length(which(is.na(rrpp$data_avail)))))` articles not producing shareable data (Figure \@ref(fig:articleScores)B).
